\Title

### 2013-08-02 supplement_body.tex
contour

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Simulations with different parameters}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.6\linewidth]{simulations_syn_gentime_2days.pdf}
\caption{
Results of simulations with alternative parameters.
Panel A) Like \figurename~4B in the main text, but simulations are performed using a
generation time of two days. Two selection coefficient of synonymous sites
doubles in units of 1/generations, hence keeps constants in units of 1/days.
}
\label{fig:sims_altparameters}
\end{center}
\end{figure}

>>>>

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Simulations with different parameters}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=0.4\linewidth]{simulations_syn_gentime_2days.pdf}\\
%\includegraphics[width=0.24\linewidth]{simulations_syn_mu_1e-5.pdf}
%\includegraphics[width=0.24\linewidth]{simulations_syn_latin_suppl.pdf}
%\includegraphics[width=0.24\linewidth]{simulations_syn_mu_3e-5.pdf}
%\includegraphics[width=0.24\linewidth]{simulations_syn_mu_4e-5.pdf}\\
%\includegraphics[width=0.32\linewidth]{simulations_syn_coi_5e-3.pdf}
%\includegraphics[width=0.32\linewidth]{simulations_syn_latin_suppl2.pdf}
%\includegraphics[width=0.32\linewidth]{simulations_syn_coi_2e-2.pdf}
%\caption{
%Results of simulations with alternative parameters.
%\textbf{Panel A)} Like \figurename~4B in the main text, but simulations are performed using a
%generation time of two days. Two selection coefficient of synonymous sites
%doubles in units of 1/generations, hence keeps constants in units of 1/days.
%\textbf{Panels B, C, D, and E)} Effect of mutation rate on the simulation
%results. The mutation rates are respectively $1 \times 10^{-5}$ (B), $2 \times
%10^{-5}$ (C), $3 \times 10^{-5}$ (D), and $4 \times
%10^{-5}$ (E) per generation per site. Increasing the mutation rate tightens the
%requirement that almost all synonymous mutations must be deleterious. This can
%be rationalized as follows: a higher $\mu$ increases the neutral synonymous
%diversity (we have measured this directly in our simulations), hence more and
%more synonymous SNVs that reach high frequency are neutral and the
%effect of deleterious SNVs, although present, becomes too weak to be observed as
%a depression in $P_\text{fix}$. As a consequence, only simulations with almost
%no neutral sites still show a reduced $P_\text{fix}$ and are shown in the
%figures.
%\textbf{Panels F, G, H)} Effect of recombination rate on the simulation results.
%The recombination rates are respectively $0.5 \times 10^{-5}$ (F), $10^{-5}$
%(G), and $2 \times 10^{-5}$ (H) per generation per site. Recombination does not
%change the results qualitatively in terms of fixation probability. Simulations
%with high recombination rates, however, have an excessively high synonymous
%diversity compared to the data (dots at the bottom and right side of panel H).
%More stringent gating around the data solves this issue.
%}
%\label{fig:sims_altparameters}
%\end{center}
%\end{figure}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Marginal distributions in simulations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.99\linewidth]{simulations_syn_marginals.pdf}
\caption{
Marginal distributions of parameters in simulations that reproduce the
synonymous fixation probability and diversity seen in the data. The prior on all
parameters are flat lines (see methods). Whereas some parameters do not seem to
affect the fixation of synonymous deleterious SNVs (e.g. the recombination
rate), the effect of deleterious synonymous changes and their abundance are
crucial, as discussed in the main text.
}
\label{fig:sims_altparameters}
\end{center}
\end{figure}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Divergence and diversity over time in simulations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.6\linewidth]{simulations_diversity_divergence_example.pdf}
\caption{
Diversity and divergence over time in an example simulation with realistic
parameters. Divergence from the founder genotype accumulates linearly. On the
contrary, because of the frequent selective sweeps of escape mutations, diversity saturates
relatively quickly. The population dynamics after that point is in a steady
state.
}
\label{fig:sims_altparameters}
\end{center}
\end{figure}
